Topological Graph Theory

### 2019-04-14 Topology/Paper/paper.tex
Hi
updates

\subsection{History}
%TODO add more to section
The seven bridges of K\"onigsberg problem was solved by Euler %TODO Citation (wikipedia for seven bridges of konigsberg)
in 1736. In mathematics this problem is of great historical significance as it is considered to be the beginning of graph theory as well as a sort of precursor to topology. %TODO Citation

@@

@@

\section{Kuratowski's Theorem}
\begin{theorem}[Kuratowski's Theorem]
	A graph $G$ is planar if and only if it does not contain any subgraph $H$ such that a some series of edge contractions on $H$ would produce $K_5$ or $K_{3,3}$.
\end{theorem}

Here $K_5$ refers to the complete graph on 5 verticies, and $K_{3,3}$ is the complete bipartite graph with three verticies in both partitions. Drawings of both theses graphs are below with ($K_5$ on left and $K_{3,3}$ on right).
\begin{center}
	\begin{tikzpicture}[auto, node distance=3cm, every loop/.style={},
	thick,main node/.style={circle,draw,font=\sffamily\Large\bfseries}]

@@

The basic sketch of the proof will be:
\begin{enumerate}
	\item Prove that $K_5$ and $K_3,3$ are not planar.
	\item Prove that if if a graph $G$ is planar than any graph obtained through an edge contraction is also planar.
	\item 
\end{enumerate}

>>>>

\subsection{History}
%TODO Make how short this is less obvious
The seven bridges of K\"onigsberg problem was solved by Euler %TODO Citation (wikipedia for seven bridges of konigsberg)
in 1736. In mathematics this problem is of great historical significance as it is considered to be the beginning of graph theory as well as a sort of precursor to topology. %TODO Citation

@@

\subsection{Subdivision}
%TODO rename unsubdivide
\def\unsubdivide{vertex replacement}
\def\unsubdividepl{vertex replacements}

To define this we first describe, we first have to describe an operation where we take a vertex $v$ that has degree 2, and replace with an edge as follows.

\begin{center}
	$
	\begin{array}{l}
		\begin{tikzpicture}[auto, node distance=3cm, every loop/.style={},
		thick,main node/.style={circle,draw,font=\sffamily\Large\bfseries}]

		\node[main node] (1) {$v$};
		\node[main node] (2) [left of=1] {$A$};
		\node[main node] (3) [right of=1] {$B$};

		\path[every node/.style={font=\sffamily\small}]
		(1)	edge node {} (2)
		edge node {} (3);
		\end{tikzpicture}
	\end{array}
	$
	\scalebox{2}{$\to$}
	$
	\begin{array}{l}
		\begin{tikzpicture}[auto, node distance=3cm, every loop/.style={},
		thick,main node/.style={circle,draw,font=\sffamily\Large\bfseries}]

		\path[every node/.style={font=\sffamily\small}]
		(1)	edge node {} (2);
		\end{tikzpicture}
	\end{array}
	$

	or

	$
	\begin{array}{l}
		\begin{tikzpicture}[auto, node distance=3cm, every loop/.style={},
		thick,main node/.style={circle,draw,font=\sffamily\Large\bfseries}]

		\node[main node] (1) {$v$};
		\node[main node] (2) [left of=1] {$A$};
		\node[main node] (3) [right of=1] {$B$};

		\path[every node/.style={font=\sffamily\small}]
		(1)	edge node {} (2)
		edge node {} (3)
		(2) edge [bend left] node {} (3);
		\end{tikzpicture}
	\end{array}
	$
	\scalebox{2}{$\to$}
	$
	\begin{array}{l}
		\begin{tikzpicture}[auto, node distance=3cm, every loop/.style={},
		thick,main node/.style={circle,draw,font=\sffamily\Large\bfseries}]

		\path[every node/.style={font=\sffamily\small}]
		(1)	edge node {} (2);
		\end{tikzpicture}
	\end{array}
	$

	\scalebox{.9}{Here $A$ and $B$ may be connected in any way to a larger graph, however only this subgraph will change.}
\end{center}

Now we are going to call this operation \unsubdivide, and using it we define a graph subdivision as follows.

\begin{definition}[graph subdivision]
	A graph $G$ is a subdivision of $H$ if $H$ may be produced by some series of \unsubdividepl\ on $G$.
\end{definition}

@@

\section{Kuratowski's Theorem}
\begin{theorem}[Kuratowski's Theorem]
	A graph $G$ is nonplanar if and only if it contains a subgraph that is a subdivision of $K_{3,3}$ or $K_5$
\end{theorem}

%TODO Maybe explanation of what $K_5$ and $K_{3,3}$ are should be earlier?
Here $K_5$ refers to the complete graph on 5 vertices, and $K_{3,3}$ is the complete bipartite graph with three vertices in both partitions. Drawings of both theses graphs are below with ($K_5$ on left and $K_{3,3}$ on right).
\begin{center}
	\begin{tikzpicture}[auto, node distance=3cm, every loop/.style={},
	thick,main node/.style={circle,draw,font=\sffamily\Large\bfseries}]

@@

\subsection{$K_{3,3}$ and $K_5$}
Our first step is proving that $K_{3,3}$ and $K_5$ are nonplanar. To do this we are going to use the following theorem.

\begin{theorem}[Euler's formula on planar graphs]
	For any plane drawing of a graph, we have $$v-e+f=2$$, where $v$ is the number of vertices in the graph, $e$ is the number of edges in the graph, and $f$ is the number of faces in the plane drawing of the graph.
\end{theorem}
%TODO credit this to https://www.ics.uci.edu/~eppstein/junkyard/euler/interdig.html
Before we can prove this we need to define the dual of a planar graph.
\begin{definition}[graph dual]
	For any plane drawing $G$ of a graph, we may construct it's dual $G*$ by putting a single vertex in each face, and putting an edge between any two adjacent faces (faces that share an edge). Note that this dual is not necessarily a graph, but will fit our definition of a multigraph.
\end{definition}
For example consider the following graph drawing
\input{Duals_graphs.tex}

\begin{proof}

\end{proof}
